\chapter{Research Plan}
\label{chapter:research_plan}
This chapter is dedicated to the presentation of the research project. In Section \ref{sec:research_topic}, the \textit{Research Topic} will be described. Specifically, starting from the state of the art presented in Section \ref{sec:sota}, which contains a comprehensive overview with respect to the Learning from Demonstration problem, the context of interest will first be identified, going on to describe the application scenario in which the proposed system will be placed. Next, the reference approach currently used to solve the Learning from Demonstration problem given the scenario of interest will be identified. Finally, based on the considerations made earlier, some research gaps will be identified, highlighting how current methods partially solve these gaps and proposing some hints on how advances can be made based on the current state of the literature.
In Section \ref{sec:research_activity} the \textit{Research Plan} will be described. Specifically, starting from the gaps reported in the previous section, the proposed hints will be formalized, defining hypotheses of methods and procedures that can lead to their implementation, and pointing out why the proposal can improve the current literature. Next, the experimental techniques that will be followed to evaluate and compare the proposed methods will be described.

\input{Chapters/2_research_plan/2_1_research_topic.tex}
\input{Chapters/2_research_plan/2_2_proposed_research_activity.tex}