\subsection{Compulsary courses}
The mandatory courses supported were:
\begin{itemize}
    \item Scientific Writing and Publishing. The course is focused on presenting the metrics used to assess the goodness of author, paper, and scientific journal. The course ended with the review and comparison of two scientific articles, brought as examples of a well-written and a poorly written article, according to the guidelines presented during the course. 
    \item Advanced Machine Learning. The course aims to present advanced aspects, both theoretical and practical, related to modern Machine Learning techniques. It ended with a project in which a Deep Network was designed, trained and validated to solve the facial attribute multi-class classification problem.
    \item Optimization Techniques for Engineers. The course aims to present the theoretical aspects needed to model, solve, and evaluate real world problems by leveraging optimization techniques. It ended with a project in which the presented optimization techniques have been used to formulate and solve a trajectory planning problem.
    \item Computational Paradigms for problem solving. The course presents the Logic Programming paradigm and the Functional Programming paradigm, related to the more general declarative paradigm. During the course, exercises were conducted through which it was possible to analyze and solve problems using the paradigms presented, thus understanding their importance and the main differences from the more well-known Imperative Paradigm.
    \item English Language C1.
\end{itemize}